Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-12-10 batchdedup/eval.tex

>>>>

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Rounds},
		ylabel={Backup Cost},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
                legend pos=north west
		]
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.5+\thisrow{DBP2jobspan}*0.5)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.7+\thisrow{DBP2jobspan}*0.3)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{DBP2avgbackup}*0.9+\thisrow{DBP2jobspan}*0.1)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.5+\thisrow{BPLjobspan}*0.5)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.7+\thisrow{BPLjobspan}*0.3)] {figures/packing_comparison.txt};
                \addplot table[x=Rounds,y expr=(\thisrow{BPLavgbackup}*0.9+\thisrow{BPLjobspan}*0.1)] {figures/packing_comparison.txt};
                \legend{DBP2 $\alpha=.5$, DBP2 $\alpha=.7$, DBP2 $\alpha=.9$, BPL $\alpha=.5$, BPL $\alpha=.7$, BPL $\alpha=.9$};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup Cost for DBP2 and BPL. TODO:reformat this graph}
  \label{fig:cost-comparison}
\end{figure}
